---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Ilze"
date: "25 January 2023"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

* This pitch and shiny application was built for the "Developing Data Products" assignment.

<br /><br />

* The developed shiny app for this assignment is avalilable in this presentation and at: https://ilze777.shinyapps.io/ShinyApp/

<br /><br />

* The source codes of ui.R and server.R and also the presentation are available on the GitHub repo: 
https://github.com/Ilze777/-Developing-Data-Products-Week-4-Course-Project

## Parabola

**Formula**
<br />$y = \text{'Stretch or compress'} * (\text{'X intercept'} - x)^2 + \text{'Y intercept'}$

<br />
**Stretch or compress**

* Strech (> 1.0) or compress (< 1.0) parabola
* Value between 0.2 and 1.8

<br />
**X intercept**

* Vertex position on the x axis
* Value between -10 and 10

<br />
**Y intercept**

* Vertex position on the y axis
* Value between -10 and 10

## Shiny App: Parabola
**Sidebar panel**

* sliderInput for Stretch or compress (min=0.2, max=+1.8, step=0.2)

* sliderInput for X Intercept (min=-10, max=+10, step=0.5)

* sliderInput for Y Intercept (min=-10, max=+10, step=0.5)

<br /><br />
**Main panel (ggplot)**

* Title contains the customized parabola formula

* Customized parabola (blue)

* Marked vertex of customized parabola (red)

* Normal parabola and its vertex (light grey)

## Shiny App: Example

```{r}
knitr::include_app("https://ilze777.shinyapps.io/ShinyApp/", height = "450px")
```
The developed shiny app for this assignment is also avalilable at: https://ilze777.shinyapps.io/ShinyApp/
